\begin{thebibliography}{0}

% stosowanie_modelu.pdf
\bibitem{kinematic_modeling}
P. Muir, C. Neuman,
``Kinematic modeling for feedback control of an omnidirectional wheeled mobile robot'', 
Proceedings, IEEE International Conference in Robotics and Automation, 
Vol 4. pp. 1772-1778, 1987.

% koła.pdf
\bibitem{wheels}
M. O. Tătar, C. Popovici, D. Mândru, I. Ardelean, A. Pleşa,
``Design and development of an autonomous omni-directional mobile robot with Mecanum wheels'',
Conference: 2014 IEEE International Conference on Automation, Quality and Testing, Robotics,
Cluj-Napoca, 2014, pp. 1-6. DOI: 10.1109/AQTR.2014.6857869.

% paletobot.pdf
\bibitem{paletobot}
M. Lamy, 
``Mechanical development of an automated guided vehicle'',
Master of Science Thesis MMK 2016:153 MKN 171,
KTH Industrial Engineering and Management,
Machine Design.

% matematyka_rolki.pdf
\bibitem{rollers}
A. Gfrerrer, 
``Geometry and kinematics of the Mecanum wheel'',
Computer Aided Geometric Design,
25(9):784-791.

% silny_robot.pdf
\bibitem{heavy}
L. Xie, C. Scheifele, W. Xu, K. A. Stol, 
``Heavy-Duty Omni-Directional Mecanum-Wheeled Robot for Autonomous Navigation'',
2015 IEEE International Conference on Mechatronics (ICM), Nagoya, 2015, pp. 256-261.
DOI: 10.1109/ICMECH.2015.7083984.

% hamowanie.pdf
\bibitem{braking}
V. Kálmán, 
``On modeling and control of omnidirectional wheels'',
PhD. dissertation, Budapest University of Technology and Economics,
Department of Control Engineering and Information Technology,
Budapeszt 2013.

% ruchome_osie.pdf
\bibitem{extra_axis}
J.B. Song, K.S. Byun,
``Design and Control of a Four-Wheeled Omnidirectional Mobile Robot with Steerable Omnidirectional Wheels'',
Journal of Robotic Systems,
21(4):193-208, 
Kwiecień 2004.

% jakiśtam.pdf
\bibitem{boringbot}
I. Doroftei, V. Grosu, V. Spinu,
``Omnidirectional Mobile Robot – Design and Implementation'',
Bioinspiration and Robotics Walking and Climbing Robots, M. K. Habib (Ed.), 
ISBN: 978-3-902613-15-8, InTech,
2007.

% sposoby_modelowania.pdf
\bibitem{modelling_ways}
V. Kálmán,
``Omnidirectional Wheel Simulation --- a Practical Approach'',
Acta Technica Jaurinensis,
6(2):73-90,
2013.

\bibitem{gazebo_website}
Strona internetowa symulatora Gazebo. \\
\url{http://gazebosim.org}

\bibitem{vrep_website}
Strona internetowa symulatora V-Rep. \\
\url{http://coppeliarobotics.com}

\bibitem{ros_website}
Strona internetowa programowej struktury ramowej \emph{Robot Operating System}. \\
\url{http://www.ros.org}

\bibitem{sdf_website}
Strona internetowa standardu SDF. \\
\url{http://sdformat.org/spec}

\bibitem{sick_website}
Strona internetowa SICK, producenta czujników laserowych. \\
\url{https://www.sick.com/de/en/detection-and-ranging-solutions/2d-lidar-sensors/lms1xx/lms100-10000/p/p109841}

\bibitem{adis_website}
Strona internetowa sprzedawcy czujnika inercji. \\
\url{https://www.digikey.com/product-detail/en/analog-devices-inc/ADIS16460AMLZ/ADIS16460AMLZ-ND/5957823}

\bibitem{ode_contact}
Dokumentacja ODE z wyjaśnieniem działania kolizji. \\
\url{http://ode-wiki.org/wiki/index.php?title=Manual:_Joint_Types_and_Functions#Contact}

\end{thebibliography}
